SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-10-28 docs/questioning.tex
minor change

In the case of JavaScript-driven {\sc xss} attacks
the various countermeasures follow a similar pattern.
{\it {\sc swap}}~\cite{WPLKK09} follows a similar approach
with {\sc didafit} and creates a unique identifier
({\it script {\sc id}}) for every legitimate script on the server.
Then, a JavaScript detection component placed in a
web proxy (locus {\sc y}) searches for injected scripts
with no corresponding {\sc id} in the server's responses.
If no injected scripts are found, the proxy forwards the
request to the client.
% dimitro: more mechanisms TBA.

>>>>

In the case of {\sc xss} attacks the various countermeasures
follow a similar pattern. {\it {\sc swap}}~\cite{WPLKK09}
creates a unique identifier ({\it script {\sc id}}) for
every legitimate script on the server.
Then, a JavaScript detection component placed in a
web proxy (locus {\sc y}) searches for injected scripts
with no corresponding {\sc id} in the server's responses.
If no injected scripts are found, the proxy forwards the
request to the client.
% dimitro: more mechanisms TBA.
